### 2019-10-31 thesis/txt/3-data-set.tex
various small fixes, citing webpages
bigger data sets for meta-parameter optimization

\section{Labeling}
\subsection{Output Examples: Build Failure Reason}
We labeled the first occuring substring describing the failure.
If there were multiple errors described we took the first continuous block of error description.

@@

\begin{figure}[h]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/dev-mails/answers-received.pdf}
		\caption{Proportions of Mails and Logs answered, undelivered and unanswered}
		\label{fig:mails-answers-received}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/dev-mails/extraction-correct.pdf}
		\caption{Responses to our developer survey}
		\label{fig:mails-extraction-correct}
	\end{minipage}
\end{figure}

\subsubsection{Results}
In total we sent out mails to 246 developers, asking about 3.2 build logs on average.
32 of these mails could not be delivered, e.g. because they were addressed at noreply mail addresses.
These 32 mails related to 68 of the build logs.
We received answers from 61 developers, responding about 144 build logs.
The proportions of mails and logs answered about, not delivered and unanswered is shown in Figure \ref{fig:mails-answers-received}.

>>>>

\section{Labeling}
\subsection*{Output Examples: Build Failure Reason}
We labeled the first occuring substring describing the failure.
If there were multiple errors described we took the first continuous block of error description.

@@

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/dev-mails/answers-received-mails.pdf}
		\caption{Proportions of Mails answered, unanswered, not delivered and no mail found}
		\label{fig:mails-answers-received-mails}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/dev-mails/extraction-correct.pdf}
		\caption{Responses to our developer survey}
		\label{fig:mails-extraction-correct}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/dev-mails/answers-received-builds.pdf}
		\caption{Proportions of Logs answered, undelivered and unanswered}
		\label{fig:mails-answers-received-builds}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/dev-mails/logs-per-mail.pdf}
		\caption{Responses to our developer survey}
		\label{fig:mails-logs-per-mail}
	\end{minipage}
\end{figure}

\subsubsection{Results}
In total we sent out mails to 246 developers, asking about 3.2 build logs on average.
32 of these mails could not be delivered, e.g. because they were addressed at noreply mail addresses.
These 32 mails related to 68 of the build logs.
We received answers from 61 developers, responding about 144 build logs.
The proportions of mails and logs answered about, not delivered and unanswered is shown in Figure \ref{fig:mails-answers-received-mails} and Figure \ref{fig: mails-answers-received-builds}.
